Add Plant Functional Type labels

### 2021-03-09 R/add_plant_functional_type.Rmd
try TRY next?
maybe taxize package has what we need?

```{r}
#usda_plants <- read_csv(file.path(here::here(), "analysis", "data", "usda_plants_20160713.csv"),
                        local = locale(encoding = "latin1"))

@@

>>>>

```{r}
#usda_plants <- read_csv(file.path(here::here(), "analysis", "data", "usda_plants_20160713.csv"))

@@

## TRY Database

https://www.try-db.org/TryWeb/Home.php

## Taxize

https://www.rdocumentation.org/packages/taxize/versions/0.9.99
